Results

### 2023-03-17 06_Paper/ER-ED/ERED_Stage2/Results.Rmd
added descr table

To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator* and *Levator* activity. 
We found a highly significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures successfully evoked emotional arousal and physiological responding.<!--JZ: Am besten auch die Richtung angeben, also "...valence for an increase in subjective..."-->

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, *Corrugator* and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression). 
We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc tests, please see tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).

@@

[INSERT TABLE 1 HERE]

@@

The predictors effort rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2)$full_result$Corr_cwc`) showed a significant association with SVs.
The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
Interestingly, utility rating showed the greatest effect size of all predictors ($f^{2}=$ `r papaja::printnum(H5_M2_table[4,5], digits = 3)`), indicating that utility rating explained `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.<!--JZ: Mir wurde mal die Verwendung von Worten wie "interestingly" im Ergebnisteil angekreidet, also die Bewertung vielleicht bis zum Diskussionsteil aufheben-->
Effort rating showed an effect size of $f^{2}=$ `r papaja::printnum(H5_M2_table[2,5], digits = 3)`.
The effect sizes of all other predictors were negligibly small ($f^{2}< 0.01$).

>>>>

To explore whether negative pictures evoke emotional arousal and physiological responding, we conducted separate ANOVAs for the active viewing condition with predictors subjective arousal, *Corrugator* and *Levator* activity.
Descriptive values of each predictor for each condition can be found in table \@ref(tab:TabDescr).
We found a highly significant main effect of valence for subjective arousal (`r papaja::apa_print(SubjArousalView_aov)$full_result`, `r papaja::apa_print(SubjArousalView_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrView_aov)$full_result`, `r papaja::apa_print(EMGCorrView_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevView_aov)$full_result`, `r papaja::apa_print(EMGLevView_BF)$statistic`), indicating that negative pictures successfully increased emotional arousal and physiological responding.

To investigate whether ER strategies reduce emotional arousal and physiological responding, we conducted separate rmANOVA comparing subjective arousal, *Corrugator* and *Levator* activity of four strategies (active viewing, distraction, distancing, suppression). 
We found a significant effect of strategy for subjective arousal (`r papaja::apa_print(SubjArousalReg_aov)$full_result`, `r papaja::apa_print(SubjArousalReg_BF)$statistic`), *Corrugator* activity (`r papaja::apa_print(EMGCorrReg_aov)$full_result`, `r papaja::apa_print(EMGCorrReg_BF)$statistic`), and *Levator* activity (`r papaja::apa_print(EMGLevReg_aov)$full_result`, `r papaja::apa_print(EMGLevReg_BF)$statistic`), indicating that regulation strategies reduced subjective arousal and physiological responding.
For detailed information on post-hoc tests, please see tables \@ref(tab:SupplEffectArousalReg) to \@ref(tab:SupplEffectLevReg) and figures \@ref(fig:SupplFigArousalReg) to \@ref(fig:SupplFigLevReg) in the [supplementary material](#SupplementEffectER).
[INSERT TABLE 1 HERE]

``` {r TabDescr, echo=FALSE, message=FALSE, warning=FALSE}
papaja::apa_table(
  df.descr,
  caption = "$M \\pm SD$ of subjective arousal, subjetive effort, subjective utility, Corrugator activity, and Levator activity for each condition.",
  booktabs = TRUE,
  escape = FALSE,
  placement = "H")
```

@@

[INSERT TABLE 2 HERE]

@@

The predictors effort rating (`r papaja::apa_print(MLM_2)$full_result$effort_cwc`), utility rating (`r papaja::apa_print(MLM_2)$full_result$utility_cwc`), and *Corrugator* activity (`r papaja::apa_print(MLM_2)$full_result$Corr_cwc`) showed a significant association with SVs.
The values were relatively small, so the respective effect size $f^{2}$ was calculated as the explained variance.
The predictor utility rating showed the greatest effect size of all predictors ($f^{2}=$ `r papaja::printnum(H5_M2_table[4,5], digits = 3)`), indicating that utility rating explained `r papaja::printnum(H5_M2_table[4,5]*100, digits = 1)`% of variance in SVs.
Effort rating showed an effect size of $f^{2}=$ `r papaja::printnum(H5_M2_table[2,5], digits = 3)`.
The effect sizes of all other predictors were negligibly small ($f^{2}< 0.01$).
